\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\usepackage{fancyhdr}
\pagestyle{fancy}

\lhead{Gill, Surinder
		1308896\\
		Hu, Joshua
		1311940\\
		Lago, Nick
		1302613}
\rhead{\today}

\title{Problem Statement}
\author{}
%\date{}							% Activate to display a given date or no date
%\begin{header}

%\end{header}
\begin{document}
%\maketitle
\marginpar{}
\section*{Problem Statement}
\subsection*{What problem are you trying to solve?}

\newcommand*\apos{\textsc{\char13}}
Many people around the world are seeking a means of entertainment, and some achieve this through video games. As game developers, we\apos re trying to create a fun and innovative game for the general public to enjoy. The game we are trying to recreate was solely available for mobile devices. However, we\apos re implementing it for web browsers and creating new platforms for people to play an incredibly popular mobile device game for free.

\subsection*{Why is this an important problem?}

Now that the original game, FlappyBird, is no longer available on the mobile device application market, we\apos ve created a way for people to play it once again. FlappyBird was an extremely popular game that was removed from the application market by its original developer and it received millions of downloads and reviews daily at its prime. However, after its removal, many people were unable to share their high scores with other people. By recreating a free web application that allows multiple users to play this game, we\apos ve allowed for people to dive into the fun and entertainment that FlappyBird provides once again. 

\subsection*{What is the context of the problem you are solving?}

Our recreation of FlappyBird is a game that can be played by all ages and is not limiting in its platforms. Almost every device is able to access a web browser and run JavaScript. This creates an environment for users to play the game for free and without any downloads allowing for a more accessible way to play this game than previously available.

\end{document}  